A Handbook for Tenured Track Faculty in Computer Science in the US

### 2024-08-27 demystify.tex
updates

  \item[SOP] Statement of Purpose. A document written by yourself to explains your research interests, background, and reasons for applying to a PhD program (\autoref{sec:sop}).

@@

  \item [PI]  Principal Investigator. A lead researcher on a grant or research project, e.g., a PI on an NSF grant. Prospective students often use this term to refer to a professor they are interested in working with.  While this term is used frequently in online forums among students, we do not use it this way in academia, e.g., ``who is your PI?'' might only make sense to fellow Reddit applicants, but might not be understood by others, ``who is your adviser?'' is what you want to use.
    \item[STEM] Science, Technology, Engineering, and Mathematics. A term used to group together these academic disciplines. CS is considered a STEM field.
  \item[URM] Underrepresented Minority. Refers to groups that are underrepresented in higher education, e.g., Black, Hispanic, and Native American students.
  \item[NSF] National Science Foundation. A US government agency that supports research and education in science and engineering. NSF is a major source of funding for RAs in CS research. There are other agencies that support RAs but they might require US citizenship or permanent residency.
        \item [R1/R2 Universities] Research 1 (R1) universities are universities with the highest level of research activity. Research 2 (R2) universities have a high level of research activity but not as high as R1 universities.  R1 universities are typically more prestigious and have more funding and resources for research.  R2 universities are also good but might have fewer resources and funding.
  \item [Rolling Admission] A process where applications are reviewed as they are received, and decisions are made throughout the admission cycle.  This is in contrast to a process where all applications are reviewed after the deadline and decisions are made at the same time. Rolling admission is more common for MS programs and less common for PhD programs (e.g., at Mason, MS is rolling and PhD is not).
  \item [Top-tier conferences and journals] These are the most prestigious venues for publishing research in CS.  For example, in Software Engineering, top-tier conferences include ICSE, FSE, and ASE and top-tier journals include TSE and TOSEM.  Publishing in these venues is highly competitive and prestigious, and can significantly improve your chances of getting admitted to a good PhD program.

@@

  \section{Miscs}\label{sec:cultural-misc}
  Several other common surprises for international students (and foreigners in general) in the US:

  \paragraph{Healthcare System}  You (and your spouse) will need health insurance! Otherwise you will be charged a lot for healthcare services. However, as mentioned in \autoref{sec:funding}, your  TA/RA  will cover health insurance (and your spouse/children also get insurance or discount for it). However, be aware that heathcare services can still be expensive even with insurance. So  know what your insurance covers and be prepared for unexpected costs.  Moreover, healthcare system has many confusing jargons such as HMO, PPO, deductibles, copays, and coinsurance.  Get yourself familiar with them and ask for help when needed.

  \paragraph{Tipping Culture} Unlike many other countries, tipping is expected for various services, especially in restaurant. So adding an extra 15--20\% to your bills is common, especially in restaurants.
  You should also tip for other services, e.g., Uber, taxi, haircuts, and hotel services.  The minimum wage for tipped employees is lower than the standard minimum wage, so tips are an important part of their income.  If you do not tip, it is considered rude and disrespectful.

@@

	%\paragraph{Individualism} The strong culture of individualism in the US can be both liberating and isolating. People are more focused on their personal rights and tend to be less concerned with what others think.

>>>>

  \item[Q1 journal] Commonly mentioned by international students to refer to top-tier journals in CS.  This is not a standard in CS in the US (which often focuses on confs. rather than journals), and many CS faculty in the US might not know what this means.  If you want to refer to top-tier journals, you should mention the specific journals, e.g., TSE in Software Engineering.

  \item[SOP] Statement of Purpose is a document written by yourself to explains your research interests, background, and reasons for applying to a PhD program (\autoref{sec:sop}).

@@

  \item [PI]  Principal Investigator is lead researcher on a grant or research project, e.g., a PI on an NSF grant.  Prospective students often use this term to refer to a professor they are interested in working with.  However, we do not use it this way in academia, e.g., ``who is your PI?'' might only make sense to fellow Reddit applicants, but might not be understood by others, ``who is your adviser?'' is what you want to use.
    \item[STEM] Science, Technology, Engineering, and Mathematics. A term used to group together these academic disciplines. CS is considered a STEM field.
  \item[URM] Underrepresented Minority. Refers to groups that are underrepresented in higher education, e.g., Black, Hispanic, and Native American students.
  \item[NSF] National Science Foundation. A US government agency that supports research and education in science and engineering. NSF is a major source of funding for RAs in CS research. There are other agencies that support RAs but they might require US citizenship or permanent residency.
        \item [R1/R2 Universities] Research 1 (R1) universities are universities with the highest level of research activity. Research 2 (R2) universities have a high level of research activity but not as high as R1 universities.  R1 universities are typically larger, and have more funding and resources for research.  R2 universities are also good but might have fewer resources and funding.

        \item [Rolling Admission] Applications are reviewed as they are received (instead of all at once after the deadline), and decisions are made throughout the admission cycle.  Rolling admission is more common for MS programs and less common for PhD programs (e.g., at Mason, MS is rolling and PhD is not).

  \item [Top-tier conferences and journals] These are the most prestigious venues for publishing research in CS.  For example, in Software Engineering, top-tier conferences include ICSE, FSE, and ASE and top-tier journals include TSE and TOSEM.  Publishing in these venues is highly competitive and prestigious, and can significantly improve your chances of getting admitted to a good PhD program.

@@

  \section{Miscs}\label{sec:cultural-misc}

  Several other common surprises for international students (and foreigners in general) in the US. Note that I skip topics involving politics, religion, tax, and racism as these happen in many countries and are not unique to the US.

  \paragraph{Small talks} People often engage in small talks, e.g., about the weather, sports, or weekend plans.  This is a way to start a conversation and how social interaction starts in the US.

  Moreover, avoid asking personal questions, e.g., about salary, age, relationship status, or health, as these are considered private (talking about kids' activities or schools are OK). Also, do not talk about politics or religion in general (in fact, we often do not talk about these with our family and friends to avoid conflicts).  Sometimes foreigners are surprised by how Americans do not talk about their personal lives, e.g., sharing details about their families, health, or relationships, and that their conversations are often not very ``deep'' or ``mind-provoking''. This is just a cultural norm about privacy and personal space.

  \paragraph{Healthcare System}  You (and your spouse) will need health insurance! Otherwise you will be charged a lot for healthcare services. However, as mentioned in \autoref{sec:funding}, your  TA/RA  will cover health insurance (and your spouse/children also get insurance or discount for it).

  However, be aware that heathcare services can still be expensive even with insurance. So  know what your insurance covers and be prepared for unexpected costs.  Moreover, healthcare system has many confusing jargons such as HMO, PPO, deductibles, copays, and coinsurance (try take a look at the Explanation of Benefits or EoB statement you received from your insurance company). It's arguably the most complicated system in the US and even Americans often do not understand it (and politicians often exploit this to their advantage).  So do not hesitate to ask your HR or the insurance company for help.

  \paragraph{Tipping Culture} Unlike many other countries, tipping is expected for various services, especially in restaurant. So adding an extra 15--20\% to your bills is common, especially in restaurants.
  You should also tip for other services, e.g., Uber, taxi, haircuts, and hotel services.  The minimum wage for tipped employees is lower than the standard minimum wage, so tips are an important part of their income.

@@

	%\paragraph{Individualism} The strong culture of individualism in the US can be both liberating and isolating. For example, Americans are encouraged to express their opinions and pursue their goals, and are more focused on their personal rights (e.g., they do not want people do things in front of their house).

### 2024-08-27 faculty.tex
updates

This is a cultural issue and is very difficult to change. Many good researchers have left such places because of this.  However, some were able to leverage this and publish at easy places and do really well within their department.  However, while they thrive at such places, they will likely not get funding and recognition in their field.  This is a trade-off that you need to consider.

@@

\chapter{Teaching}

\section{From a P\&T Point of View}

While teaching should take about 40\% of your time (equivalent to research) and your salary is mainly for teaching, teaching is not as nearly as important as research for tenure.  Moreover, for most new faculty, teaching is not as difficult as getting grants or publishing papers. Thus, tenure-track faculty often do not worry much about teaching.

\section{Teaching Load}
\section{Teaching Evaluation}

>>>>

This is a cultural issue and is very difficult to change. Many good researchers have left such places because of this.  Some were able to leverage this and publish at easy places and do really well within their department.  However, while they thrive at such places, they will likely not get funding and recognition in their field.  This is a trade-off that you need to consider.

@@

\chapter{Teaching}\label{chapter}

While teaching should take about 40\% of your time (equivalent to research) and your salary is mainly for teaching, it is not as nearly as important as research for tenure.  Moreover, for most new faculty, teaching is not as difficult as getting grants or publishing papers, and thus is often taken lightly by new faculty.  However, teaching is still important for your tenure case, and being a good teacher can be very rewarding. Moreover, innovative integration of research and teaching can help you win good students and even NSF grants.

\section{Teaching Load}
New TT faculty often have a lighter teaching load in their first several years or even throughout their tenure track.  This is to give you time to establish your research program.  However, you should expect to teach at least one course per semester.  The teaching load is usually higher at teaching universities, and lower at research universities. At some universities, you might be able to buy out of teaching by getting a grant.

\section{Teaching Evaluation}
